How and Why to run a Hack Week

### 2017-12-06 sections/conclusions.tex
Added some correlation searches to paper

As introduced above, hack weeks serve multiple purposes, including dissemination of state-of-the-art technological advances through the scientific community, building collaborations between academic subdisciplines and fostering interdisciplinary research as well as  promoting open science and reproducibility.
Initial results from three events held in 2016 in three different fields (astronomy, geosciences and neurosciences) indicate that hack weeks succeed at all of these objectives, but that the measure of success is field-specific in that it depends to some degree on how much the concepts hack weeks promote were already adopted within the community.
Hack weeks are still a very young concept, and estimating the long-term impact of these events within the scientific communities they serve will require follow-up over multiple years to asses their effect on collaboration networks, career outcomes for early-career academics and adoption of new methods.
We have shown, however, that hack weeks provide an easy-to-implement, fairly low-cost method to introduce new technologies and methods into scientific fields on much shorter time scales than traditional teaching efforts can.

>>>>

As introduced above, hack weeks serve multiple purposes, including dissemination of state-of-the-art technological advances through the scientific community, building collaborations between academic subdisciplines and fostering interdisciplinary research as well as  promoting open science and reproducibility.
Initial results from three events held in 2016 \textbf{and 2017} in three different fields (astronomy, geosciences and neurosciences) indicate that hack weeks succeed at all of these objectives, but that the measure of success is field-specific in that it depends to some degree on how much the concepts hack weeks promote were already adopted within the community.
Hack weeks are still a very young concept, and estimating the long-term impact of these events within the scientific communities they serve will require follow-up over multiple years to asses their effect on collaboration networks, career outcomes for early-career academics and adoption of new methods.
We have shown, however, that hack weeks provide an easy-to-implement, fairly low-cost method to introduce new technologies and methods into scientific fields on much shorter time scales than traditional teaching efforts can.

### 2017-12-06 sections/results.tex
Added some correlation searches to paper

Focusing on the outcomes of astro-, geo- and neuro- hack weeks (AHW, GHW, NHW, respectively) from 2016, we find that \textbf{most} participants self-report successful learning outcomes in new topics, tools or methods (AHW: 76\%, GHW: 89\%, NHW: 79\% for responses ``somewhat agree'', ``agree'' and ``strongly agree''; Figure \ref{fig:survey}, top panel, left).
The overwhelming majority of respondents at the hack weeks ($>95\%$ for all three events) believed that they learned things that improve their day-to-day research, and that attendance has made them a better scientist ( Figure \ref{fig:survey}, top panel, right and middle).
%While each hack week also probed participants' attitudes in more detail toward specific topics, methods, and modes of learning, the hack weeks differed substantially on that level, making the results difficult to compare.
%Another important goal of the hack weeks was centred on community building and fostering collaborations.
The majority of participants felt that their contributions to their hack teams was valued, and that they built valuable connections to other researchers (Figure \ref{fig:survey}, middle panel, middle).
This is especially true for Neuro Hack Week, where more than 64\% of participants strongly agreed that they formed valuable connections at NHW (Figure  \ref{fig:survey}, middle panel, right).
Because peer learning is a major mode of knowledge transfer at hack weeks, we asked participants whether they taught other participants.
We find that again a majority agrees with this statement to some degree (AHW: 79\%, GHW: 69\%, NHW: 75\% for combined responses ``somewhat agree'', ``agree'' and ``strongly agree''; Figure \ref{fig:survey}, middle panel, left), though responses are not as unequivocal as they are in some of the other categories.
This is expected: participants new to the field may participate to learn rather than to teach.

>>>>

Focusing on the outcomes of astro-, geo- and neuro- hack weeks (AHW, GHW, NHW, respectively) from 2016, we find that \textbf{most} participants self-report successful learning outcomes in new topics, tools or methods (AHW: 76\%, GHW: 89\%, NHW: 79\% for responses ``somewhat agree'', ``agree'' and ``strongly agree''; Figure \ref{fig:survey}, top panel, left).
The overwhelming majority of respondents at the hack weeks ($>95\%$ for all three events) believed that they learned things that improve their day-to-day research, and that attendance has made them a better scientist ( Figure \ref{fig:survey}, top panel, right and middle).
%While each hack week also probed participants' attitudes in more detail toward specific topics, methods, and modes of learning, the hack weeks differed substantially on that level, making the results difficult to compare.
%Another important goal of the hack weeks was centred on community building and fostering collaborations.
The majority of participants felt that their contributions to their hack teams was valued, and that they built valuable connections to other researchers (Figure \ref{fig:survey}, middle panel, middle).
This is especially true for Neuro Hack Week, where more than 64\% of participants strongly agreed that they formed valuable connections at NHW (Figure  \ref{fig:survey}, middle panel, right).
Because peer learning is a major mode of knowledge transfer at hack weeks, we asked participants whether they taught other participants.
We find that again a majority agrees with this statement to some degree (AHW: 79\%, GHW: 69\%, NHW: 75\% for combined responses ``somewhat agree'', ``agree'' and ``strongly agree''; Figure \ref{fig:survey}, middle panel, left), though responses are not as unequivocal as they are in some of the other categories.
This is expected: participants new to the field may participate to learn rather than to teach. \textbf{It is notable, however, that we find no correlation between the response to this question and career stage for any of the events surveyed here. In particular, participants from all career stages between graduate students and tenured faculty report similar engagement in teaching. This supports our hypothesis that compared to e.g.\ a traditional summer school, a hack week is less hierarchical and encourages lateral knowledge transfer between participants at different career stages.  We similar find no correlations with gender identity or race/ethnicity. Responses to the other two questions regarding whether participants' contributions to hack teams were valued and whether they made valuable connections at the hack week were similarly evenly distributed across career stages, gender and racial/ethnic identities.}
